An Extensible Approach to Verification of Embedded Systems

### 2014-05-02 tech-project/implementation.tex
fixed minor bugs

Any model seeking to convert RESOLVE to a lower level representation such as C demands a strategy for handling memory utilized by the generated code. While dynamic allocation is typically the norm, it is not however the first choice for embedded applications. With the Telosb mote constrained to 128 bytes of RAM, developers targeting embedded platforms tend to favor static memory allocation over dynamic, due the memory efficiency it affords.

>>>>

Any model seeking to convert RESOLVE to a lower level representation such as C demands a strategy for handling memory utilized by the generated code. While dynamic allocation is typically the norm, it is not however the first choice for embedded applications. With the Telosb mote constrained to 10kB of RAM, developers targeting embedded platforms tend to favor static memory allocation over dynamic, due the memory efficiency it affords.
